### 2021-08-05 paper/paper.tex
ARW: PID and Gingerbread results (#7)
* added gingerbread man example figures and reproducibility instructions

* fixed figure spacing in gingerbread results

* better reference to the mesh sub figure

* forgot to update the README now that HOHQMesh is used directly using a control file

* ignore output files of HOHQMesh

* Apply some suggestions from code review

Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>

* adjust file paths in control file for consistency

* added Manifest for the gingerbread man runs

Co-authored-by: Hendrik Ranocha <mail@ranocha.de>
Co-authored-by:

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{TODO: Plot of this comparison with the \lstinline{TreeMesh}?}

\todo{TODO: Add MHD results?}

>>>>

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

\todo{TODO: Add MHD results}

@@
